Initial Analysis

### 2019-11-28 Initial_Analysis.Rmd
Trying to get the RFMO analysis right

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
}
if(Sys.info()[7] == "hall1000"){
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
}

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- paste(here::here(),"/Temporal_Data",sep = "")
}
if(Sys.info()[7] == "hall1000"){
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
}
